H0LiCOW: correlation between black hole mass and host galaxy luminosity.

### 2020-02-22 manuscript/manuscript.tex
Update tex and upload figure

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}

@@

\section{Sample Selection}
We adopt the eight lens systems from our H0LiCOW collaboration including HE~0435$-$1223, RXJ~1131$-$1231, WFI~2033$-$4723, HE~1104$-$1805, SDSS~1206$+$4332, SDSS~0246$-$0825, HE~0047$-$1756 and HS~2209$+$1914. For conciseness, we abbreviate each lens name to four digits (e.g., RXJ~1131$-$1231 to RXJ1131). In \citet{Ding2017a}, the simulation exercise has been performed to understand the fidelity of the source reconstruction based on these eight systems and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN. The detailed information for the information of these eight systems are given in Table~1 therein. Besides, half of the systems, including HE0435, RXJ1131, WFI2033 and HE1104 have \hst\ imaging data in multi-bands. To estimate the \mbh, we adopt the spectra information as inferred by \citet{Sluse2012, Peng2006, Shen2011}. We use a Table[] to summarize the data information. \ding{table should including the redshift, filter/Camera, the drizzled pixel size.}

@@

We adopt a class of consistent recipes as introduced in~\citet{Ding2020} to estimate the \mbh\ of our sample. \ding{Do we want to include the detailed information here?}

@@

\subsection{Model Choice}
We carry out the fitting process to subtract the central AGN light, constrain the lens model, and reconstruct the host galaxy in the source plan, simultaneously.
We assume the photometry of the galaxies (including the lensing galaxy and source galaxy) is described by the 2-D elliptical \sersic\ profile. We start with a single \sersic\ and consider to use two \sersic\ if any significant residual indicate a multiply component. By this definition, we could infer the host flux as consistent to our comparison sample. The bright AGNs are unsolved and modelled by a scaled point spread function (PSF). We adopt the elliptical power-law model to describe the surface mass density of the deflector. An external shear component is also considered.

We employ the imaging modelling tool \lenstronomy~ref[] to perform the fitting task. The input ingredients include the lensing imaging data, noise level map and a PSF, as is described by~\citet{Ding2020}. We draw the image mask for each systems to define the region in which the pixels would to be included in the likelihood. For any objects which is close to the lens, we model its light as one extended source described by \sersic\ profile.

@@

For a lens system with a number of $N$ initial PSFs, there are in total $N\times12$ (i.e., $2 \times2 \times3$) fittings. After the all sets of fittings are completed, we rank the performance of each choice based on their best-fitted $\chi^2$ value. We adopt the weighting algorithm as introduced by ~\citet{Ding2020} and combine the top eight choices to derive the final inference.

\subsection{Photometry Inference}
In this section, we describe the details of the fitting for each systems and present the corresponding inference of the host photometry information.

%remember to present a table to summarize the fitting results. The inference of the observed magnitude, Reff and sersic. 
\subsubsection{HE0435}
This system has been modeled.

We choose five isolated stars in this field to input as the initial PSFs. 
Comparison to the previous inference.
The fitting image and inferred parameter, including: Einstein Radius, host n, host Reff, host flux, host flux ratio.

@@

@@

\subsubsection{WFI2033}

@@

\ding{Do we consider the Selection effect? We only select 8 sample? Maybe we only over plot them together and see if the results are self-consistent?}

>>>>

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{subfig} %for figure subplot

@@

\section{Sample Selection}
We adopt the eight lens systems from our H0LiCOW collaboration including HE~0435$-$1223, RXJ~1131$-$1231, WFI~2033$-$4723, HE~1104$-$1805, SDSS~1206$+$4332, SDSS~0246$-$0825, HE~0047$-$1756 and HS~2209$+$1914. For conciseness, we abbreviate each lens name to four digits (e.g., RXJ~1131$-$1231 to RXJ1131). In \citet{Ding2017a}, the simulation exercise has been performed to understand the fidelity of the source reconstruction based on these eight systems and verified that the host inference is trustworthy when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN. The detailed information for the information of these eight systems are given in Table~1 therein. Besides, half of the systems, including HE0435, RXJ1131, WFI2033 and HE1104 have \hst\ imaging data in multi-bands. To estimate the \mbh, we adopt the spectra information as inferred by \citet{Sluse2012, Peng2006, Shen2011}. We use a Table[] to summarize the data information. \ding{table should include the redshift, filter/Camera, the drizzled pixel size.}

@@

We adopt a class of consistent recipes as introduced in~\citet{Ding2020} to estimate the \mbh\ of our sample. \ding{Do we want to include the detailed information such as recipe and the other things here?}

@@

\subsection{Model Choice}
We carry out the fitting process to subtract the central AGN light, constrain the lens model, and reconstruct the host galaxy in the source plan, simultaneously.
For all the systems, we assume the photometry of the galaxies (including the lensing galaxy and source galaxy) is described by the 2-D elliptical \sersic\ profile. We start with a single \sersic\ and consider to use two \sersic\ if any significant residual indicate a multiply component. For single \sersic\ case, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical inference. By this definition, we could infer the host flux as consistent to our comparison sample. The bright AGNs are unsolved and modelled by a scaled point spread function (PSF). We adopt the elliptical power-law model to describe the surface mass density of the deflector. An external shear component is also considered.

We employ the imaging modelling tool \lenstronomy~ref[] to perform the fitting task. We following the standard procedure as introduced by~\citet{Ding2020} to produce the fitting ingredients including the lensing imaging data, noise level map and the PSF condition. We draw the image mask for each systems to define the region in which the pixels would to be included in the likelihood.

@@

For a lens system with a number of $N$ initial PSFs, there are in total $N\times12$ (i.e., $2 \times2 \times3$) fittings. After the all sets of fittings are completed, we rank the performance of each choice based on their best-fitted $\chi^2$ value. We adopt the weighting algorithm as introduced by ~\citet{Ding2020} and combine the top eight choices to derive the final inference and estimate the uncertainties.

\subsection{Photometry Inference}
In the result of this section, we describe the details of the fitting for each systems and present the corresponding inference of the host photometry information.

%remember to present a table to summarize the fitting results. The inference of the observed magnitude, Reff and sersic. 
\subsubsection{HE0435}
We follow Ken[] and assuming light of the deflector are composed of two elliptical \sersic\ with index value $n$ fixed to $1$ and $4$ to represent the disk and bulge components

We select five isolated stars in this field initial PSFs to input to the fitting thus, we have in total 60 fittings for this case. The best-fit models are present in the Figure~\ref{fig:image_inference}-(a). Using the top eight inference, we use weighting to combining them and inferred the results. 
The fitting image and inferred parameter, including: Einstein Radius, host n, host Reff, host flux, host flux ratio.

Note that the residual maps are appears to be less ideal than the ones as presented by Ken[]. The major reason is the definition of the host galaxy. We compare the result with the inferred host galaxy by Ken[] and Ding+2017.

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
\subfloat[HE0435]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0435_best_inference.pdf}}&
\subfloat[RXJ1131]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/RXJ1131_best_inference.pdf}}\\
\subfloat[WFI2033]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/WFI2033_best_inference.pdf}}&
\subfloat[SDSS1206]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS1206_best_inference.pdf}}\\
\subfloat[HE1104]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE1104_best_inference.pdf}}&
\subfloat[SDSS0246]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/SDSS0246_best_inference.pdf}}\\
\subfloat[HS2209]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HS2209_best_inference.pdf}}&
\subfloat[HE0047]{\includegraphics[trim = 40mm 25mm 40mm 25mm, clip, width=0.5\textwidth]{fig/HE0047_best_inference.pdf}}\\
\end{tabular}
\caption{\label{fig:image_inference} 
Something}
\end{figure*}

@@

\subsubsection{WFI2033}
The objects which is close to the lens, we model its light as one extended source described by \sersic\ profile.

@@

%\ding{Do we consider the Selection effect? We only select 8 sample? Maybe we only over plot them together and see if the results are self-consistent?}
